\documentclass[12pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry} % Adjusts the margins to reduce blank space

\signature{}
\address{}
\date{}

\begin{document}

\begin{letter}{}
To Whom It May Concern,

I have been working as a full stack developer with Intel for the past 5 years. With a career that has spanned remote collaborations across India and Costa Rica, and different time zones of PST, MST, CST, and EST, I’ve honed my ability to work seamlessly with diverse teams and adapt to varied workflows—a skill I believe aligns perfectly with the globally connected environment at Stack Overflow.

My passion for software development goes beyond just writing code; for me, it’s about continuous learning and problem-solving. I’ve spent countless hours not just building applications but also diving deep into emerging technologies, exploring better ways to structure systems, and contributing to collaborative coding communities. This aligns deeply with Stack Overflow’s mission to empower developers worldwide.

What draws me most to Stack Overflow is its commitment to fostering a community where developers can grow, share, and learn together. My proudest achievements at Intel were always based around my love of learning best practices: implementing flexible, reusable backend libraries supporting generics; incorporating GoF design patterns to avoid reinventing the wheel while supporting clean code with composition over inheritance in mind; building CI/CD pipelines from scratch to enhance automated infrastructure; and eliminating legacy front-end code with poor practices by replacing it with better implementations guided by the principle of Inversion of Control. All of my accomplishments were made possible thanks to the foundational work and iterations of the online developer community. I want to be a part of the team that directly supports this wonderful collaboration.

Thank you for considering my application. I would be delighted to discuss how my background and passions align with the needs of your team. I look forward to the opportunity to contribute to Stack Overflow’s mission.

\closing{Best regards,\\[1em] Kevin D. Kim}

\end{letter}

\end{document}
